Total Score

### 2022-11-14 src/MSAtotal_scores.Rmd
cr3eating rmd for total score; reading in real estate and landlord score

```{r}
# read in the data
category_score_data <- read_sheet(https://docs.google.com/spreadsheets/d/1zu6ta_gI5lF3l2RC5eE3BuUsywYg8gd6xcMfuTKb9Bk/edit#gid=852316062)

>>>>

```{r}
# read in the data
real_estate_score_data <- read_sheet("https://docs.google.com/spreadsheets/d/1Ssmb7pUd4NFZocVp9C75SRMOV6tAJCCt0TjrCYBB8pY/edit#gid=2007178520")

landlord_score_data <- read_sheet("https://docs.google.com/spreadsheets/d/1nLpDhM88a3rEBDVK5RZlk2B6QuwVIwvsfE5HeBz0mLo/edit#gid=983090810")
